News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex
update

As input we consider a high volume of articles in different languages. By using a language detector the stream is split into separate monolingual streams. 
The documents are semantically annotated and linked across languages by using a cross-lingual similarity measure. Within each monolingual stream, an online
clustering approach is employed, where tracked clusters correspond to events. Finally, using

  and using the cross-lingual techniques  as well as processed using standard text mining techniquesBy using an online clustering approach

@@

Event Registry works by collecting and analyzing news articles that are published by news outlets in different languages all over the world. Collected articles are first semantically annotated by identifying in them mentions of relevant concepts -- either entities or important keywords. The disambiguation and entity linking of the concepts is done using Wikipedia as the main knowledge base.
   The key step in Event Registry is then to apply an online clustering algorithm on the articles in order to identify groups of articles that are discussing the same event.

   Within this system, we test our multilingual similarity measures as well as our algorithms for matching clusters across languages.  The result is that we can test total performance in a multilingual, real-world setting.

>>>>

As input we consider a high volume of articles in different languages. By using a language detector the stream is split into separate monolingual streams. 
Within each monolingual stream, an online clustering approach is employed, where tracked clusters correspond to our definition of events - this is based on the Event Registry system \shortcite{Leban2014W,Leban2014I}. Our main goal is to connect such clusters (representations of events) across languages, that is detect that a set of documents in language 1 reports on the same event as a set of documents in language 2.

Our approach to combines two ingredients: a cross-lingual document similarity measure, which can be interpreted as a language independent topic model, and
semantic annotation of documents, which enables an alternative way to comparing documents by comparing the lists of detected semantic entities.

The first approach represents a continuation of previous work \shortcite{nips,sikdd,nips2,iti} where we explored representations of documents which were valid over multiple languages.  The representations could be interpreted as multi-lingual topics, which were then used as proxies to compute cross-lingual similarities between documents. To learn the representations, we use Wikipedia as a training corpus. Significantly, we do not only consider the major or \emph{hub} languages such as English, German, French, etc. which have significant overlap in article coverage, but also smaller languages (in terms of number of Wikipedia articles) such as Slovenian and Hindi, which may have a negligible overlap in article coverage. We can then define a similarity between any two articles regardless of language,  which allows us to cluster the articles according to topic. The underlying assumption being that articles describing the same event are similar  and will therefore be put into the same cluster.

@@

%
%Event Registry works by collecting and analyzing news articles that are published by news outlets in different languages all over the world. Collected articles are first semantically annotated by identifying in them mentions of relevant concepts -- either entities or important keywords. The disambiguation and entity linking of the concepts is done using Wikipedia as the main knowledge base.
%   The key step in Event Registry is then to apply an online clustering algorithm on the articles in order to identify groups of articles that are discussing the same event.
%
%   Within this system, we test our multilingual similarity measures as well as our algorithms for matching clusters across languages.  The result is that we can test total performance in a multilingual, real-world setting.
